Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-03 R0V0.tex
Change statement of the main result (cont.)

\begin{theorem}\label{thm:main result}
	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

>>>>

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_1\succ0,\ldots,W_N\succ0
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}
